Appendix

### 2018-06-08 manuscript/appendix.Rmd
create demo split map

library(rayshader)
library(elevatr)
library(raster)

test <- elevatr::get_elev_raster(as_Spatial(iws), z = 1)

@@

```{r best_partition_maps}
partition_splits <- read.csv("../figures/table_1.csv")
partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
                                  scale %in% c("nws", "iws"))
partition_splits <- droplevels(partition_splits)
partition_splits$pnames2 <- factor(partition_splits$pnames2, 
                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))

@@

lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
                         function(x) {
                           nes_sub <- get_sub(nes_iws, 
                                            partition_splits[x, "iws_names"],
                                            partition_splits[x, "splits"])

@@

lower_iws_maps <- lower_iws_maps[
  match(levels(partition_splits$pnames2), 
        partition_splits$pnames2[which(partition_splits$scale == "iws")])
  ]

# lower_iws_maps[1][[1]] <- lower_iws_maps[1][[1]] + 
#   theme(plot.margin = unit(c(1,0,0,0), "lines"))

@@

plot_grid(
  plot_grid(NULL,
            NULL, 
            NULL,
            NULL,
            NULL, 
            nrow = 4, ncol = 1,
            labels = c("A. LWS", "", "B. NWS", "", ""), 
            label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 
            hjust = c(-0.1, 0, -0.12, 0, 0)),
  plot_grid(
    plot_grid(plotlist = lower_iws_maps, 
                   ncol = 3, nrow = 2, align = "v"),
    plot_grid(ggplot() + geom_blank()),
    plot_grid(plotlist = lower_nws_maps,
                   ncol = 3, nrow = 2, align = "v"), 
    ncol = 1, rel_heights = c(1, 0.1, 1)), 
rel_widths = c(0.2, 1), ncol = 2)

>>>>

@@

```{r best_partition_maps, cache=TRUE}
# setwd("manuscript")

partition_splits <- read.csv("../figures/table_1.csv")
partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
                                  scale %in% c("nws", "iws"))
partition_splits <- droplevels(partition_splits)
partition_splits$pnames2 <- factor(partition_splits$pnames2, 
                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))
partition_splits <- dplyr::filter(partition_splits, d_k > 0.2)

@@

@@

@@

plot_grid(plotlist = lower_nws_maps[2],
         ncol = 1, nrow = 1, align = "v")
